---
title: "Homework 5"
author: "Eileen Shea"
date: "November 15, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

library(tidyverse)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

## Problem 1

First we create a dataframe containing all of the file names.

```{r}
df = tibble(
  file_name = list.files("./data", full.names = TRUE)
)
```

Next we iterate over file names and read in data for each subject using `purrr::map`. We will save the result as a new variable in the dataframe. 

```{r}
read_file = function(file_name) {
  read_csv(file_name)
}
```

```{r}
df_untidy =  
  df %>% 
mutate(
  file_data = map(file_name, read_file)
) 
```

Finally we need to tidy the resulting dataframe.

```{r}
df_tidy =
  df_untidy %>% 
  unnest() %>% 
  separate(file_name, c("arm", "subject"), sep = "_") %>% 
  separate(subject, c("subject_ID", "remove")) %>% 
  mutate(arm = recode(arm, "./data/con" = "control", "./data/exp" = "experimental")) %>% 
  gather(key = week, value = response, week_1:week_8) %>% 
  separate(week, c("remove2", "week"), sep = "_") %>% 
  select(-remove, -remove2) %>% 
  mutate(week = as.numeric(week)) %>% 
  arrange(arm, subject_ID)
```

With our tidy dataset we will make a spaghetti plot showing observations on each subject over time.

```{r}
df_tidy %>% 
  ggplot(aes(x = week, y = response, color = subject_ID)) +
  geom_line() +
  facet_grid(~arm)
```

Based on this plot, we see that the experimental group saw increases in response over time, while the control group generally stayed the same over time with some fluctuations by week and possibly even a slight downward trend. 

## Problem 2

First we need to read in the data.

```{r}
homicide_data = read_csv("./data/homicide-data.csv")
```

The raw data includes `ncol(homicide_data)` variables and `nrow(homicide_data)` observations; each observation represents an individual homicide case. Variables include a unique ID that incorporates location information, date the homicide was reported, victim information (last name, first name, race, age, sex), city, state, latitude and longitude of the incident, and the disposition (i.e. status) of the case. Unidentifiable characteristics are reported as 'Unknown'. 

Next we will create a `city_state` variable.

```{r}
US_hom_data = homicide_data %>% 
  mutate(state = toupper(state), city_state = str_c(city, state, sep = ", "))
```

Using this new variable, we will summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
US_hom_data %>% 
  group_by(city_state) %>% 
  summarize(n_total = n())
```

This `group_by` shows 51 distinct city-state combinations when there should only be 50; moreover, the summary data shows 'Tulsa, AL' with 1 homicide. This seems like a mistake since 1 is inconsistent with the other `n_total` numbers, and 'Tulsa, AL' is also not a real place. This observartion will be dropped and we will re-do the summary.Furthermore, we also need a variable that indicates whether a homicide was unsolved.

```{r}
US_hom_data_50 = US_hom_data %>% 
  filter(city_state != "Tulsa, AL") %>% 
  mutate(unsolved = ifelse(disposition == "Closed without arrest" | disposition == "Open/No arrest", TRUE, FALSE))

US_hom_data_50 %>% 
  group_by(city_state) %>% 
  summarize(n_total = n(), n_unsolved = sum(unsolved)) %>% 
  arrange(desc(n_total)) %>% 
  knitr::kable()
```






  

